\Title

### 2022-09-29 Grimaldi-etal-BiolCybernetics.tex
Results: 3.1

%
Finally, the output of the MLR model is an event-based representation predicting at each position and at each time the probability of each motion. Such an output gives a form of optical flow that can be exploited for non-rigid motions, but we have defined here, for simplicity, an evaluation method that applies to our task with a full field motion. We have shown above that when different independent observations (here, the estimated motion at different spatial locations) are recognized as having a common cause (here, the rigid motion of the image), then an optimal estimate of the logit of this probability is the sum of the logits of the independent probabilities. By taking the logit of the probability of the output given by the model, we can therefore calculate the probability of the output. This allows one to calculate the accuracy (as the percentage of times the motion is accurately predicted) or the squared error $|| \speed - ||^2$ of the velocity estimate given by :
$
\speed = \sum_{\class} \speed_\class \cdot Pr(\class \vert image)
$ 
These calculations are performed on a different input dataset than the one used in the training or validation steps. These metrics will be useful to compare our methods with other methods on our defined task.  The complete code to reproduce the results of this paper is available at \url{https://github.com/SpikeAI/pyTERtorch}.  
%
\section{Results}
\label{sec:results}
%%%-----------------------------------------------------------------
%: fig:kernels
%%%-----------------------------------------------------------------
\subsection{Kernels learned for motion detection}
%%%-----------------------------------------------------------------
\begin{figure*}[ht!]
    {\centering
    %\vspace{-3cm}
    \includegraphics[width=\linewidth]{figures/motion_kernels.pdf}
    }
    %\vspace{-.5cm}
    \caption{
    	Representation of the weights for the $8$ learned kernels of the model corresponding to the OFF polarities and selective to the different motion directions
	(because of the symmetry observed between the ON and OFF event streams, kernels are similar for the ON polarities). These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes.
	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown. One sees positive (excitatory) coefficients for the specific direction of motion and negative (inhibitory) coefficients for all other directions.
	}
    \label{fig:kernels}
\end{figure*} 
%
%
After training our model, we first observe the weights learned for the different neurons (\seeFig{kernels}). Focusing on the positive weights, a strong selectivity is observed along specific axes for the different kernels. These directions can be easily associated to the direction of motion controlled in the motion clouds. For instance, the third and the seventh kernels show a horizontal selectivity to motion directions.
%
With the negative weights, one can observe an anti-selectivity for directions that do not correspond to the motion to which the kernel is selective to. This qualitative look at the 3D kernels allows the reader to infer for the $8$ different motion directions used to generate our synthetic event streams.

>>>>

%
Finally, the output of the MLR model is an event-based representation predicting at each position and at each time the probability of each motion. Such an output gives a form of optical flow that can be exploited for non-rigid motions, but we have defined here, for simplicity, an evaluation method that applies to our task with a full field motion. We have shown above that when different independent observations (here, the estimated motion at different spatial locations) are recognized as having a common cause (here, the rigid motion of the image), then an optimal estimate of the logit of this probability is the sum of the logits of the independent probabilities. By taking the logit of the probability of the output given by the model, we can therefore calculate the probability of the output. This allows one to calculate the accuracy (as the percentage of times the motion is accurately predicted) or the squared error $|| \speed - ||^2$ of the velocity estimate given by :
$
\speed = \sum_{\class} \speed_\class \cdot Pr(\class \vert image)
$ 
These calculations are performed on a different input dataset than the one used in the training or validation steps. These metrics will be useful to compare our methods with other methods on our defined task.  The complete code to reproduce the results of this paper is available at \url{https://github.com/SpikeAI/pyTERtorch}.  
%
\section{Results}
\label{sec:results}
%%%-----------------------------------------------------------------
%: fig:kernels
%%%-----------------------------------------------------------------
\subsection{Kernels learned for motion detection}
%%%-----------------------------------------------------------------
\begin{figure*}[ht!]
    {\centering
    %\vspace{-3cm}
    \includegraphics[width=\linewidth]{figures/motion_kernels.pdf}
    }
    %\vspace{-.5cm}
    \caption{
    	Representation of the weights for $3$ of the $32$ different learned kernels of the model. Each corresponding to the OFF polarities and selective to the different motion directions (because of the symmetry observed between the ON and OFF event streams, we observed that kernels are very similar for the ON polarities). These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes. %	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown. 
        One sees positive (excitatory) coefficients for the specific direction of motion but also negative (inhibitory) coefficients for other directions.
	}
    \label{fig:kernels}
\end{figure*} 
%
%
After training our model, we first observe the weights learned for the different neurons (\seeFig{kernels}). Focusing on the positive weights, a strong selectivity is observed along specific axes for the different kernels. These directions can be easily associated to the direction of motion controlled in the natural images. For instance, the first kernel shows a selectivity to horizontal motion directions.
%
We observed a high dependendance between the weights reaching the ON polarities and that reaching the OFF polarities. ith the negative weights, one can observe an anti-selectivity for directions that do not correspond to the motion to which the kernel is selective to. This qualitative look at the 3D kernels allows the reader to infer for the $8$ different motion directions used to generate our synthetic event streams.
